Modeling Interventions

### 2021-03-04 paper/paper.Rmd
adding refs

Yet another possibility – again not mutually exclusive to others – is that children are getting better at using the words they know. 
Several recent studies have found that a surprising proportion of variance in the rate of young children’s vocabulary growth is accounted for by the speed with which individual children are able to process familiar words (e.g., Fernald, Perfors & Marchman, 2006; Marchman, Admas, Loi, Fernald, & Feldman, 2015). 
Children’s processing speed in these studies is measured with the looking-while-listening (LWL) paradigm (Fernald, Pinto, Swingley, Weinberg, McRoberts, 1998), in which children are presented with an onscreen array of familiar objects (e.g., a shoe and a ball), and their latency to look at a named target object (ball) is measured. 
Much of this work has been correlational, however. 
Thus, it is unclear whether children with larger vocabularies are better at processing familiar words – as one might expect based on adult processing speed results, which find faster and more accurate processing of words in adults with larger vocabularies (Mainz, Shao, Brysbaert, & Meyer, 2017), or if the ability to quickly process familiar words generalizes to being faster to learn new words, as is sometimes speculated (e.g., Law & Edwards, 2015; Peter et al., 2019). 
This latter would be a form of leverage as well.

>>>>

Yet another possibility – again not mutually exclusive to others – is that children are getting better at using the words they know. 
Several recent studies have found that a surprising proportion of variance in the rate of young children’s vocabulary growth is accounted for by the speed with which individual children are able to process familiar words (e.g., @fernald2006picking; @marchman2016early). 
Children’s processing speed in these studies is measured with the looking-while-listening (LWL) paradigm (Fernald, Pinto, Swingley, Weinberg, McRoberts, 1998), in which children are presented with an onscreen array of familiar objects (e.g., a shoe and a ball), and their latency to look at a named target object (ball) is measured. 
Much of this work has been correlational, however. 
Thus, it is unclear whether children with larger vocabularies are better at processing familiar words – as one might expect based on adult processing speed results, which find faster and more accurate processing of words in adults with larger vocabularies (Mainz, Shao, Brysbaert, & Meyer, 2017), or if the ability to quickly process familiar words generalizes to being faster to learn new words, as is sometimes speculated (e.g., Law & Edwards, 2015; Peter et al., 2019). 
This latter would be a form of leverage as well.
